### 2023-03-21 main.tex
Update main.tex

The process studied in this paper is the multi-species stirring process on the geometry of a graph. We consider the general situation where at any time and at any site a mixture of $\nu\in \mathbb{N}$, chosen among $N$ possible species (sometimes called types or colors), is present. Among these $N$ types of particles we will distinguish $N-1$ 'actual' types, labelled with $k\in \{2,\ldots,N\}$ and a 'hole', labelled with $1$. This is an arbitrary choice, indeed one could call any of the $N$ colors the hole. In the description of the dynamic this choice is not important, since one could think about the dynamic as a pure exchange of types between sites, under the constraint that the maximal occupancy at each site is $\nu$. However, studying the duality for the boundary driven case, it will be important to chose an hole type, in order to interpret the dual dynamic as absorbing, i.e. to have, eventually, an empty dual process on the graph. Furthermore, as the configuration of each site at each time is a mixture of $\nu$ particles, one could think about the hole as the only type whose occupation dependes on the occupations of all the true $N-1$ colors. In the two species case, this multi-species stirring process  is the SEP($\nu$) (see \cite{giardina2009duality}, \cite{carinci2013duality}). Indeed one of the two type is the hole (say again $1$) and its dynamics depends on the one of the true type (say 2), under the constaraint that at most $\nu$ type $2$ particles are present at a site at each time. Therefore, the dynamics can be describe only by species $2$. It is interesting to observe that, in case we stop distinguishing the colors of the true particles $\{2,\ldots,N\}$, we retrieve the SEP($\nu$), thus this multi-species stirring process seems its natural generalization.

@@

@@

\end{figure}\newline \\
{\color{blue}\textbf{Remark}: 
    We can always assign the name "empty" to one of the species of particles in the above dynamics (let's say, without loss of generality, the species 1). This species would play the role of "compensator" in the exclusion constraint, in the sense that its occupation will always be determined once we know the others, i.e. $\forall x\in V$: 
        n_{1}^{x}=\twoj-\sum_{k=2}^{N}n_{k}^{x}
    Moreover, if we set $N=2$ and $\twoj=2j$, we exactly retrieve the SEP(2j), where the empty occupation is indeed $2j-\eta_{x}$ where $\eta_{x}$ is the number of (color blind) particles in the site $x$. In this sense we can think about the stirring process as the natural generalization of the SEP(2j).}

>>>>

\subsection{Informal description}
The process studied in this paper is the {\em multi-species stirring process}. 
In words, the dynamics is described as follows. Each site
of a connected graph can host up to $\nu\in \mathbb{N}$ particles.
The particles have a {\em type} (sometimes called {\em species} or {\em color})
which can take $N$ values.
Then, the dynamics has two parts: on each edge of the graph, 
any two types are swapped at rate $1$; additionally, on each site $x$, 
a particles of a give type (if present) is replaced with a
particle of type $k$ at rate $\alpha_k^x >0$.
The swap dynamics taking place on the edges is of Kawasaki-type 
with $N$ conservation laws
(the total number of particles of each type). 
The site-dynamics is instead of Glauber-type 
and, in the long-time limit, so-called non-equilibrium
steady state sets in.

\vspace{.5cm}
\noindent
{\bf Remark:} in the following we will often consider type $1$ as a distinguished type
(called `holes'), whose number at each site is fixed by the numbers of particles 
of the remaining $N-1$ types (at the same site). It is interesting to observe that, in case we stop distinguishing the colors of the ``true'' particles of types $\{2,\ldots,N\}$, we retrieve the 
boundary-driven version of the partial symmetric exclusion process \cite{ss,carinci2013duality}.
The choice of type $1$ for the distinguished type is arbitrary and does not affect
the results. In particular, we shall see in Section \ref{sectionDuality} about duality, that
the dual process eventually has only particles of type $1$ on the graph.
Interpreting type $1$ as an hole, one can then say that the dual process voids the graph.

@@

We now give the mathematical description of the multi-species stirring process.

@@

\subsection{Reversible measures}
